\bf\mftitle

### 2011-01-21 doc/jInfer/twostep/twostep.tex
Documentation: minor repairs in Architecture and TwoStep.

\subsubsection{Trie}
TODO vektor describe trie cluster processor

>>>>

\subsubsection{Trie}
This processor takes all rules in a cluster, treats them like strings and builds a prefix tree (a ``trie") of them. More precisely, it takes the first rule and delares it to be a long branch (concatenation of tokens) in a newly created tree. After that, it adds the remaining rules one by one as branches like this: as long as it can follow an existing branch, it follows it. As soon as the newly added branch starts to differ, it ``branches off" (creates an alternation at that point) the existing tree and hangs the rest of the newly added rule there. Repeating this process creates a prefix tree describing all the rules in the cluster.
